Teaching a Class to Grade Itself using Game Theory

### 2013-09-26 Primes Write up.tex
Revised Discussion

\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item When grading, $w_i=0 \oplus w_i=1$
	\item For all students, $g_i \neq o_i$
	\item Students all share a common happiness function, $H(g)$, where $g$ represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
	\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
	\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
	\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral
	\item For a given student in $N$, that student has contact with all other students in $N$
\end{enumerate}
\subsection{Comparison}
Figure~\ref{fig:comparison} on page~\pageref{fig:comparison} shows a comparison between our mechanisms and those currently in use. As you can see, our mechanisms performs better than the others, aside from the Improved Calibration Mechanism. As can be seen in the figure, the benchmark scores of all traditional methods of grading --- peer grading, hand grading by the professor, and automated grading --- are higher than those our mechanisms. This means that traditional methods result in undesirable outcomes, either inaccurate or requiring a disproportionate amount of work.

@@

Besides making the students happier than they are in other peer grading systems, the mechanisms that result from this research also provide more accurate and legitimate grades for the students. In current peer grading schemes, it is easy for students to just ``game'' the system and fake their way through a course. Giving anonymous feedback, for example, does not encourage students to be honest, rather, it gives them a reason to be \emph{dis}honest~\cite{howaccurateispeergrading}. This allows students to dishonestly grade the work of others, as well as just give whomever they want a better grade than that person actually deserves. In our mechanisms, however, these problems are solved by removing anonymity and adding incentives to make students behave honestly, no matter who they are grading.

Aside from fixing many problems that students have with other peer grading systems, our mechanisms also address the unhappiness and inconsistency caused by the grading given out by machines. One key problem that machines have is that they always look at the same thing in a paper, meaning that they can be easily ``gamed''and fooled into thinking something is better than it acutely is~\cite{robogradingproblems}. Not only does this make the system inconsistent, but any student who is lacking something that is in the list of requirements the machine checks for can be unfairly given a poor grade, making them unhappy. By solving both of these problems with the mechanisms that were created, it has been demonstrated the peer grading, at least for the moment, is better for education that automated grading.

Not only do the mechanisms developed in this research improve upon the efficiency of automated grading systems, but they also help to remove the dominance that automated grading has placed on grading large courses. By providing a system that fixes many of the problems with current automated grading systems, these mechanisms help to show that automated grading is not the only way to solve the problem of grading online courses. Because automated grading, at the moment, is not as efficient and robust as it needs to be to prevent students from creating unfair situations, this is something that is necessary to show because automated grading is simply not good enough with today's technology.

However important the creation of these mechanisms is, arguably more important to the future development of further solutions is the creation of a realistic and robust model. Without a model, many of the mechanisms mentioned would have been impossible to create, and would certainly not work as well as they do. The creation of a model is essential in game theory as it provides the outline for how the ``players''of a given game will act under any set of circumstances. As such, by creating a good model, this research has undergone the trouble of providing a way for anyone to predict how students will behave.

Not only did this research lead to the creation of a good model, but it also led to the creation of a benchmark. The creation of a benchmark is important because it allows two mechanisms to be compared side by side, and it allows theorists to definitively determine which of these mechanisms is superior. With this, it becomes possible to compare the results of this research to the results of others, and also allows future work to be done by others. Not only does a benchmark allow the research done here to be compared to that of others, but it allows two totally independent mechanisms not derived from this research to be compared, which could lead to a universal system of evaluating peer grading systems.

Both of these are major contributions towards further developments in the field of research this problem takes place in, primarily game theory. By doing so, grading mechanisms across online courses will constantly be able to evolve and improve with contributions from anyone. By creating the benchmark and model, all mechanisms will undergo a uniform set of evaluations that will allow online course systems to determine which system is the best out of any proposals. By doing so, this research has opened up a road for many game theorists to develop and analyze new ideas that will lead to improvements in student happiness and results from online courses.

>>>>

\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item When grading, $w_i=0 \oplus w_i=1$
	\item For all students, $g_i \neq o_i$
	\item Students all share a common happiness function, $H(g)$, where $g$ represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
	\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
	\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
	\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral
	\item For a given student in $N$, that student has contact with all other students in $N$
\end{enumerate}
\subsection{Comparison}
Figure~\ref{fig:comparison} on page~\pageref{fig:comparison} shows a comparison between our mechanisms and those currently in use. As shown, our mechanisms performs better than the others, aside from the Improved Calibration Mechanism. As can be seen in the figure, the benchmark scores of all traditional methods of grading --- peer grading, hand grading by the professor, and automated grading --- are higher than those our mechanisms. This means that traditional methods result in undesirable outcomes, either inaccurate or requiring a disproportionate amount of work.

@@

Traditional peer-grading schemes are prone to student manipulation: one of the issues our approach mitigates. Because such systems make grade feedback anonymous, students can easily get away with dishonestly or inadequately grading the work of others for their own benefit. Anonymity not encourage students to be honest; it gives them a reason to be \emph{dis}honest~\cite{howaccurateispeergrading}. The removal of anonymity and the application of incentives in our methods encourage positive student behavior.

Machine grading systems are known to cause unhappiness and inconsistency: one of the problems our approach addresses. Because machines always look for the same things in each paper, students who know the criteria can fool the system~\cite{robogradingproblems}, yielding inconsistent grades. Conversely, the machine may fail to recognize alternative wordings or conceptual definitions, leading to inaccurate grades and unhappy students. The mechanisms we have created solves both these issues by using humans instead of machines.

Not only do the mechanisms developed in this research improve upon the efficiency of traditional automated and peer grading systems, but the mechanisms also fix many problems inherent in such methods. These mechanisms shed light on the alternatives to automated grading, which are more efficient and lack issues inherent in computational grading. At the moment, automated grading is not as efficient and robust as it needs to be to prevent students from creating unfair situations.

The importance of a realistic and robust model --- as well as effective mechanisms --- cannot be overstated. The creation of a model is essential in game theory as it provides the outline for how the ``players''of a given game will act under any set of circumstances. Many of the mechanisms mentioned would be impossible to create without a model. A well-defined model can easily be re-used and extended by others. As such, by creating a good model, this research has undergone the trouble of providing a way for anyone to predict how students will behave.
